%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Independent Project | C++, React | Localhost Prototype} % Subheader
    {Pathfinding Visualizer (Local Web App)} % Project title
    {} % Location
    {Sept. 2025 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented BFS, Dijkstra, and A* pathfinding in C++ and structured logic so each algorithm could be visualized and compared.}
        \item {Built a React web UI to display grid-based exploration and shortest-path results, including controls for running scenarios.}
        \item {Optimized JSON serialization by encoding cell states as index lists, nearly doubling responsive grid size from ~2,500 to ~4,800 cells.}
        \item {Organized cell-state data into data structures for average-case O(1) cell lookup, reducing step-processing latency on larger grids by ~35\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
%  \cventry
%    {Team Project | React Web App Prototype (Local)} % Subheader
%    {UTRGV Inventor-Builder Matching App (Pre-Production, Early Stage)} % Project title
%    {} % Location
%    {Feb. 2026 - Present} % Date(s)
%    {
%      \begin{cvitems}
%        \item {Setting up React/Vite project architecture and baseline UI for a UTRGV inventor-builder matching platform.}
%        \item {Defining user stories and sprint backlog for swipe matching, mutual-like logic, and direct messaging workflows.}
%        \item {Designing profile data fields and filter criteria (role, programming languages, degree level, school year) for recommendations.}
%        \item {Collaborating in Agile team workflows using GitHub branches, pull requests, merges, and merge-conflict resolution.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
  \cventry
    {Independent Project | Python, Lua | Observer Pipeline (In Progress)} % Subheader
    {Balatro AI (Observer + Live-State Exporter)} % Project title
    {} % Location
    {Mar. 2026 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Built a Python observer that reads Balatro save data and normalizes core run state including money, score, hands, discards, blind, vouchers, and shop metadata.}
        \item {Added a Steamodded-compatible Lua live-state exporter that writes compact JSON snapshots so the observer can use fresher state than save files alone.}
        \item {Created an \texttt{obs\_test.py} harness to poll state changes, capture screenshots of the Balatro window, and save timestamped observation outputs for debugging.}
        \item {Wrote contract tests around live observation parsing and formatting to stabilize the data schema while the gameplay agent is still in progress.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
