%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Independent Project | Python, Lua | (In Progress)} % Subheader
    {Balatro AI (Live-State Exporter + Runtime)} % Project title
    {} % Location
    {Mar. 2026 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {Built a Steamodded Lua exporter and Python observer pipeline that reads live Balatro game state as snapshots.}
        \item {Designed a modular runtime with explicit observer, policy, validator, and executor seams, plus a demo decision loop.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Independent Project | C++, React | Localhost Prototype} % Subheader
    {Pathfinding Visualizer (Local Web App)} % Project title
    {} % Location
    {Sept. 2025 - Feb. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented BFS, Dijkstra, and A* pathfinding in C++ and structured logic so each algorithm could be visualized and compared.}
        \item {Built a React web UI to display grid-based exploration and shortest-path results, including controls for running scenarios.}
        \item {Optimized JSON serialization by encoding cell states as index lists, nearly doubling responsive grid size from ~2,500 to ~4,800 cells.}
        %\item {Organized cell-state data into data structures for average-case O(1) cell lookup, reducing step-processing latency on larger grids by ~35\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {1st Place Hackathon | Python, Flask, PostgreSQL | Deployed on Railway} % Subheader
    {Civic Hearing Summarizer \& Public Comment Analyzer} % Project title
    {} % Location
    {Apr. 2026} % Date(s)
    {
      \begin{cvitems}
        \item {Built a Flask app that ingests public hearing transcripts via YouTube API and produces plain-language LLM summaries.}
        \item {Implemented a Groq-backed clustering service to group public comments into thematic concern areas.}
        \item {Deployed to Railway with a managed PostgreSQL database, Flask-Migrate and Alembic for schema versioning, and Gunicorn.}
      \end{cvitems}
    }

%---------------------------------------------------------
% \cventry
%   {Team Project | React, Express, SQLite | Local Prototype (In Progress)} % Subheader
%   {UTRGV Inventor-Builder Matching App} % Project title
%   {} % Location
%   {Feb. 2026 - Present} % Date(s)
%   {
%     \begin{cvitems}
%       \item {Built a React/Vite frontend with role-based routing and login/signup flows for student and business onboarding.}
%       \item {Developed an Express + SQLite backend with JSON APIs, hashed passwords, input validation, and duplicate-email handling.}
%       \item {Implemented profile creation flows and a swipe-style home feed prototype for surfacing match preferences.}
%     \end{cvitems}
%   }

%---------------------------------------------------------
\end{cventries}
